paper2_resistance_mechanisms_mixtures

### 2017-01-03 inst/documents/paper2/paper2_resistance_mechanisms_mixtures.Rmd
pap2 writing

Insecticide resistance is a problem for malaria [@Who2012][@Ranson2016] other vector borne diseases and agriculture.

>>>>

Insecticide resistance is a problem for malaria [@Who2012][@Ranson2016] other vector borne diseases [@IRAC2011] and agriculture [@FAO2012].

TODO add more stuff here or after following para about protocols for resistance management.
